A Formal Model of Checked C

### 2022-07-20 sandp23/introduction.tex
minor

However, converting existing C programs to Checked C requires considerable effort~\cite{duanrefactoring}. 
Recently, Machiry et al. developed 3C~\cite{machiry2022c} that tries to automatically convert a program to Checked C by adding appropriate pointer annotations.
However, as described in 3C, complete automated conversion is infeasible and consequently requires the developer to convert some code regions manually.
Thanks to the backward compatibility of Checked C, the partially annotated program still enjoys the benefits of spatial memory safety on those regions using only Checked pointers (i.e., checked or safe regions).
But, the unconverted code regions (or unsafe regions) can affect pointers in safe regions and violate certain assumptions leading to vulnerabilities, as demonstrated by cross-language attacks~\cite{mergendahlcross}.
%
Although the blameless proof exists~\cite{ruef2019achieving}, it does not state that spatial safety violations cannot happen in Checked regions but rather states that Checked regions~\emph{cannot be blamed for any spatial safety violations}.
For instance, a checked function expects a pointer to a buffer of five elements, but an unchecked region can call this function with a pointer to a buffer of three elements. This results in a spatial safety violation in the Checked region, but of course, the blame or the root cause is in the unchecked region.
Furthermore, since checked and unchecked regions execute in the same address space, spatial memory corruptions in unchecked regions can take down the complete program despite having checked regions.
We need an isolation mechanism to ensure that code executed as part of unchecked regions does not violate the safety guarantees in checked regions.
Such an isolation mechanism should have low/no overhead and be backward compatible (i.e., pointers should have no additional metadata), preserving the advantages of Checked C.

>>>>

This mechanism is called program partitioning~\cite{rul2009towards}, and there has been considerable work~\cite{tan2017principles, brumley2004privtrans, bittau2008wedge, lind2017glamdring, liu2017ptrsplit} in the area. Most of these techniques are~\emph{data-centric}~\cite{lind2017glamdring, liu2017ptrsplit}, wherein program data drives the partitioning. E.g., Given sensitive data in a program, the goal is to partition functions into two parts or partitions based on whether a function can access the sensitive data.
The performance overhead of these approaches is dominated by marshaling costs and depends on the usage of sensitive data.
The overhead of state-of-the-art approaches~\cite{lind2017glamdring, liu2017ptrsplit} is prohibitive and varies from 37\%-163\%.
But in our case, we want a low-overhead code-centric partitioning, where the unchecked code (or functions) should be isolated (or partitioned) from checked code. We also want the technique to co-exist and be compatible with Checked C guarantees such that the partition containing checked code should still enjoy its spatial safety.
